### 2019-11-07 report/paper.tex
Add proposed solution section

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/waldo_winter} 
    \caption{Exmaple of an image showing detections with \( (name, p, p_{ratio}) \) in red, ground truth in green}
    \label{fig:waldo-winter}
\end{figure}

\section{Proposed Solution}
Give an overview of your solution, put it in a framework. Then, detail each part in the framework.

\begin{figure}[ht]
\centering
    \includegraphics[width=14cm]{figures/coteaching.png}
    \caption{Our proposed solution.}
    \label{fig:framework}
\end{figure}

@@

\begin{figure}[]
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after kemans preprocessing (originally gray-scale, but color mapped for display purposes)}
    \label{fig:preprocessed-samples}
\end{figure}

@@

@@

We use this property to train the K-Means classifier on a sample image of the \verb|wenda| class, which only 
shows the colors red, blue, black white. However we use \( k=5 \) to classify any color not lying in these four as a separate class, and then merge 
its results with the white color class. Then these four resulting classes colored centroids are mapped to uniformly
chosen values \( v \in [0, 255] \). This drastically reduces the complexity of the input images as can be seen in the right image in \autoref{fig:preprocessed-samples},
reducing input noise when processing the images with our feature descriptor in \autoref{sec:implemenation}.

@@

\subsection{Implementation}\label{sec:implemenation}

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{figures/model_overview} 
    \caption{Schematic overview of the wlado / wenda / wizard detection pileline.}
    \label{fig:model-overview}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/waldo_winter} 
    \caption{Exmaple of an image showing detections with \( (name, p, p_{ratio}) \) in red, ground truth in green}
    \label{fig:waldo-winter}
\end{figure}

\section{Proposed Solution}
Our proposed solution has two phases: pre-processing and detection.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\linewidth]{figures/model_overview} 
    \caption{Schematic overview of the wlado / wenda / wizard detection pileline.}
    \label{fig:model-overview}
\end{figure}

In the pre-processing phase, we will take all the provided high-resolution training images and crop out the three characters using the given input bounding box annotations. Negative samples will be obtained by arbitiarily sampling regions from the images that do not overlap with the given character bounding boxes. We will scale all these images to a fixed size for simplification. We will then run k-means preprocessing on these images to map the colored sample images to grayscale values.

The details will be further discussed in \autoref{subsec:data-prep}\\

Our detection phase first involves histogramming two types of feature descriptors: gradients (HoG) and values (HoV).

HoG will be used to histogram horizontal and vertical gradients in the image, which could be quite helpful in identifying features like the horizontal stripes in Waldo and Wenda's shirts. HoV is to histogram values from a SIFT detector.

We will use our training samples to train support vector machines (SVM) as a classifier to determine whether a window is either \(Waldo, Wenda, Wizard or Negative\). The classifier will predict a probability \(p\) that a window belongs to a certain class, and a ratio \(p_ratio\) to indicate the classifier's confidence in ratio to the other classes.

Afterwhich, we will perform non-maximum supression to rermove overlapping windows by choosing the one with the highest probability in each group.

Finally, the resulting boxes with the class label will be drawn on the image with the value of its probability and ratio.

The details will be further discussed in \autoref{subsec:implementation}\\

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.4\linewidth]{figures/preprocess_waldo} 
    \hspace{1cm}
    \includegraphics[width=0.4\linewidth]{figures/kmeans_waldo} 
    \caption{Preprocessed sample images for the waldo class. The left images are cropped and scaled to \( 128 \times 128 \) pixels.
    To the right the same images are shown after kemans preprocessing (originally gray-scale, but color mapped for display purposes)}
    \label{fig:preprocessed-samples}
\end{figure}

@@

We use this property to train the K-Means classifier on a sample image of the \verb|wenda| class, which only 
shows the colors red, blue, black white. However we use \( k=5 \) to classify any color not lying in these four as a separate class, and then merge 
its results with the white color class. Then these four resulting classes colored centroids are mapped to uniformly
chosen values \( v \in [0, 255] \). This drastically reduces the complexity of the input images as can be seen in the right image in \autoref{fig:preprocessed-samples},
reducing input noise when processing the images with our feature descriptor in \autoref{subsec:implementation}.

@@

\subsection{Implementation}\label{subsec:implementation}
